The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-12-30 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated compareFPT section

o4 = false
\end{MyVerbatim}
}
\smallskip

\noindent \textcolor{red}{Alternative to the next two paragraphs:}

\textcolor{blue}{Within the \emph{TestIdeals} package, the functions \texttt{testIdeal} and \texttt{FPureModule} are used to compute the test ideals of $f$ at different parameters.
By comparing test ideals of $f$ at different parameters, we can decide  whether $t$ is the $F$-pure threshold of $f$. 
Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.}

\noindent \textcolor{red}{Another possibility:}

\textcolor{blue}{
   The general method applied calls upon functionality from the \emph{TestIdeals} package.
   The test ideals $\tau(f^t)$ of $f$ vary discretely with the parameter $t$; the function \texttt{FPureModule} in \emph{TestIdeals} is used  to compute the ``last'' test ideal of $f$ with parameter in the interval $[0,t)$.
   Comparing this with the test ideal $\tau(f^t)$, computed by the function \texttt{testIdeal}, we can determine whether $t$ is an $F$-jumping number of $f$, or more specifically, the $F$-pure threshold of $f$.
}

The general method applied calls upon functionality from the \emph{TestIdeals} package.
The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used to compute the test ideals $\tau(f^t)$ and $\tau(f^{t-\varepsilon})$, for $0<\varepsilon\ll 1$.
By comparing these test ideals, we can decide whether $t$ is the $F$-pure threshold of $f$.
For instance, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ at the origin if and only if $\tau(f^t)$ is contained in the homogeneous maximal ideal, but $\tau(f^{t-\varepsilon})$ is not.

Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.

>>>>

o4 = false
\end{MyVerbatim}
}

\smallskip

The general method applied calls upon functionality from the \emph{TestIdeals} package.
   The test ideals $\tau(f^t)$ of $f$ vary discretely with the parameter $t$; the function \texttt{FPureModule} in \emph{TestIdeals} is used  to compute the ``last'' test ideal of $f$ with parameter in the interval $[0,t)$.
   Comparing this with the test ideal $\tau(f^t)$, computed by the function \texttt{testIdeal}, we can determine whether $t$ is an $F$-jumping number of $f$, or more specifically, the $F$-pure threshold of $f$.

% The general method applied calls upon functionality from the \emph{TestIdeals} package.
% The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used to compute the test ideals $\tau(f^t)$ and $\tau(f^{t-\varepsilon})$, for $0<\varepsilon\ll 1$.
% By comparing these test ideals, we can decide whether $t$ is the $F$-pure threshold of $f$.
% For instance, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ at the origin if and only if $\tau(f^t)$ is contained in the homogeneous maximal ideal, but $\tau(f^{t-\varepsilon})$ is not.
% 
% Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.
